---
title: "ESM 262 HW 3"
author: "Lauren Kaapcke"
date: "May 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r tools, include = F}

library(tidyverse)
library(stringr)

```

1. Write a function that summaries fish catches for different locations that takes as input

*a table that has prices for different fish

* a table that has the number caught for each fish species for each location

* each location is in a different column

* each fish is in a different row 

```{r tables, include = F}

# Create first table for fish prices
# Create vectors for the types of fish and prices
fish <- sample(c("Salmon", "Steelhead", "Shark", "Tuna", "Cod"))

prices <- sample(1:15, 5, replace=TRUE)

# Bind the vectors into a table
fish_prices <- cbind(fish, prices)
#fish_prices

# Create second table for number of fish caught in each location
# Create a vector of locations
locations <- sample(c("Reef", "Pier", "Beach", "River", "Lake", "Ocean"))

# Create a vector for catch numbers
catch <- sample(0:100, 6, replace=TRUE)
catch

# Repeat this vector for each fish type and store the info in a table
fish_catch <- matrix(nrow = length(fish), ncol = length(locations))
for (i in 1:length(fish)) {
  fish_catch[i,] = sample(0:100, 6, replace=TRUE)
}
#fish_catch

catches <- as.data.frame(fish_catch)
rownames(catches) <- fish
colnames(catches) <- locations
#catches

```



Function output will be

* most frequently caught fish in each location

* total revenue for each location

* total fisheries revenue sum

* if user requests it graph of revenue by location and total revenue (as text)



2. Write a second function estimates fish growth rate as a function of temperature, using the following equation from Bjoornsson et al., 2007

"The relationship between specific growth rate (G) and temperature in °C (T) estimated by a third order polynomial (G=a+bT+cT**2+d*T**3 ), where a,b,c,d and are parameters

3.  In an R markdown document

Generate some example data for your fish market function; and show how this is created and used 

Show an example of using your growth rate function with parameters from Experiment A of Table 2 in Bjoornsson et al., 2007

4. Create a package that contains your two functions and a sample data set for the the fish market function

5. Make sure all functions and the data set are documented

6. Provide at least one test for each function

7.  Export your function, 

8.  Include package and Rmarkdown in a git repository and submit the link 